%\documentclass{article}
%\usepackage{fixltx2e}
%\usepackage{amsmath}
%\begin{document}
\subsection*{}
\textbf{Definition-1: Uncertain Frequent Pattern} Given DB = \emph{\{T\textsubscript{1}, T\textsubscript{2}, T\textsubscript{3} . . . T\textsubscript{N} \}} , an uncertain database with \emph{N} transactions where minimum expected support threshold is $\delta$. The problem is to mine frequent item-sets \emph{FI} $\subset$ DB, where $ExpSup(FI_i) \geq \delta $ and $FI_i \in FI$.
\subsection*{}
\textbf{Definition-2 : Batch} A group of consecutive transactions from a transaction \emph{DB}inserted in \emph{US-tree} at a time. Let table-\ref{table:uncertain_stream_transaction} batch size = \emph{3}. \emph{T\textsubscript{1}, T\textsubscript{2}, T\textsubscript{3}} is one batch and its batch-1. Then next three \emph{T\textsubscript{4}, T\textsubscript{5}, T\textsubscript{6}} is one batch and its batch-2.
\subsection*{}
\textbf{Definition-3 : Window} Window is the size of batch consecutive one \emph{US-tree} can hold. Let table-\ref{table:transaction_batch} be an example of grouped transaction and batch number tagged. So for window size \emph{2} The in a certain time batch-1 and batch-2 will create a window. then after some times when batch-3 comes then batch-2 and batch-3 will create the next window.
\subsection*{}
\textbf{Definition-4 : U\textsuperscript{cap}} The following equation is for cap calculation.
\input{example/eqn_cap}
\\
For transaction \emph{DB} example in table-\ref{table:uncertain_stream_transaction} for \emph{T\textsubscript{1}}, \emph{U\textsuperscript{cap}} of \emph{a{0.9}} is $0.9$ as a is the first item. For \emph{c(0.6)} \emph{U\textsuperscript{cap}} is $0.9*0.6=0.45$, \emph{d(0.50)} \emph{U\textsuperscript{cap}} is $0.9*0.5=0.45$ and \emph{e(0.2)} \emph{U\textsuperscript{cap}} is $0.9*0.2=0.18$. \emph{U\textsuperscript{cap}} is the upper bound of existential probability. As we are taking the max of all previous items coming in a particular order all items or item sets having existential probability must be less than or equal \emph{U\textsuperscript{cap}}. that is $\forall(i,j)\{ P(I_i)*P(I_j)\leq U_{cap}(I_j)\}$ where $i < j$. So support must be less than or equal \emph{U\textsubscript{cap}}.
%
%\end{document}