\chapter{Conclusions}
\lhead{Chapter 5. \emph{Conclusions}}
\section{Research Summary}
In this thesis, we have proposed new sliding window based probabilistic strategy for finding frequent patterns from uncertain dynamic data. We have proposed \emph{U\textsuperscript{cap}}, which is the upper bound of existential probability. We have proposed new \emph{US-tree} data-structure that is very compact. For mining, we have introduced \emph{USFP-growth} algorithm that will efficiently and recursively mine frequent patterns from \emph{US-tree}.\\
\\
For calculating \emph{U\textsuperscript{cap}} value, we have taken upper-bound of existential probability that makes the node sharing possible between same items. For uncertainty property of data, node sharing was very much irregular in existing approaches. In our strategy, node sharing is possible more frequently and this makes the tree more compact and efficient. Our proposed \emph{US-tree} is very compact for possible node sharing much more than existing tree structures (e.g. \emph{SUF-growth} ~\cite{suf_growth}). To handle the stream of data we have proposed to divide the whole transactions into batches and windows that is completely dependent on the system user how much recent data she/he wants to store in the tree. Instead of keeping the support we have kept new meta-information based on \emph{U\textsuperscript{cap}} value that helps further mining. We have developed new algorithm \emph{USFP-growth} mining algorithm that efficiently remove unnecessary patterns from the tree earlier, which helps to improve runtime time efficiency. Conditional candidate tree needed to be mined in our approach, will be less than other approaches. This makes the mining algorithm faster. We have also introduced an efficient strategy to remove the false positives generated by our algorithm. Our comprehensive result study shows that total time (tree construction, tree mining, and false positive reduction) is less than existing approaches (e.g. \emph{SUF-growth} ~\cite{suf_growth}). We also developed a frequent pattern tree which may later be used to mine closed patterns and maximal patterns.
\section{Limitations and Scope of Future Studies}
As the frequent pattern mining over the domain of uncertain stream data is a very new, there are some scopes to extend and use our proposed approach as a tool for further research.\\ 
\textbf{Firstly,} we have introduced probabilistic model for calculating \emph{U\textsuperscript{cap}} value. This value can be studied and updated to find both upper and lower bound of existential probability.\\
\textbf{Secondly,} as data-set we have worked on is the stream data, which is dynamic, can be changed dynamically with time. Once an item comes to the top of the \emph{US-tree} stays there at least it becomes oldest data although may be very much infrequent in the recent data. This case may make the tree not compact that was possible. As data stream cannot be read more than once. So no previously assumption can be done to the tree. So some re-construction after new batch inserted into the window will possibly be the one of the major optimization of the tree.