%% ----------------------------------------------------------------
%% Thesis.tex -- MAIN FILE (the one that you compile with LaTeX)
%% ----------------------------------------------------------------

% Set up the document
\documentclass[12pt,a4paper,oneside]{csedu}  % Use the "Thesis" style, based on the ECS Thesis style by Steve Gunn
\graphicspath{{Figures/}}  % Location of the graphics files (set up for graphics to be in PDF format)

% Include any extra LaTeX packages required
\usepackage{graphicx}
\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX comments
\usepackage{vector}  % Allows "\bvec{}" and "\buvec{}" for "blackboard" style bold vectors in maths
\hypersetup{urlcolor=black, colorlinks=true}  % Colours hyperlinks in blue, but this can be distracting if there are many links.
\usepackage{amsthm}
\usepackage{array}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{fixltx2e}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{todonotes}
\usepackage[]{algorithm2e}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}

%% ----------------------------------------------------------------
\begin{document}
\frontmatter      % Begin Roman style (i, ii, iii, iv...) page numbering

% Set up the Title Page
\title{An Efficient Approach for Mining Frequent Pattern over Uncertain Data Stream}
\authors  %{\texorpdfstring
         %{\href{your website or email address}{Name}}
{Md. Badi-Uz-Zaman Shajib  \\Exam Roll: Curzon Hall-- 1089\\Registration No: EK - 899}
%{Your name should not appear on the external copies, write name between braces on the left}


%      {Author Name}
%   }
%\addresses  {\groupname\\\deptname\\\univname\\\FACULTY}  % Do not change this here, instead these must be set in the "Thesis.cls" file, please look through it instead, add roll, session and registration number ehich starts at line 204.
%\date       {\today}
%\subject    {}
%\keywords   {}

\maketitle

%% ----------------------------------------------------------------

\setstretch{1.5}  % It is better to have smaller font and larger line spacing than the other way round

% Define the page headers using the FancyHdr package and set up for one-sided printing
\fancyhead{}  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
\lhead{}  % Clears the left side page header

\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers

%% ----------------------------------------------------------------
% Declaration Page required for the Thesis, your institution may give you a different text to place here
\Declaration{

\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
I declare that this thesis titled, \emph{"An Efficient Approach for Mining Frequent Pattern over Uncertain Data Stream"} and the work presented in it are my own. This work was done wholly or mainly while in candidature for a research degree at this University. Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated. Where I have consulted the published work of others, this is always clearly attributed. Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work. I have acknowledged all main sources of help. Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip


%\begin{tabular}{lp{1in}r}
%\\ & \\ & \\


\begin{tabular}{c c c c}

  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
  Countersigned &\hspace{.50in} & & Signature \\

   & & &  \\
  \ldots\ldots\ldots\ldots \ldots\ldots\ldots\ldots   & & & \ldots\ldots\ldots\ldots \ldots\ldots\ldots\ldots   \\
  (Mohammad Samiullah, Lecturer) & & & (Md. Badi-Uz-Zaman Shajib) \\
  {\bf Supervisor} & & &  \\

 

\end{tabular}
}

\clearpage  % Declaration ended, now start a new page



% The Abstract Page
\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{
Knowledge is power. In modern times, knowledge discovery in big data is one of the most recent, interesting and popular topic for researchers. In this topic, frequent patterns finding in the large database is one of the first and important challenges. With the rapid growth of modern technology like internet, smart devices (e.g. smart phones, smart watch, smart car etc.) huge data is flowing each and every microsecond. Moreover, the incoming stream of data is not always accurate and precise. Properties of data stream flow changing each and every time with the change of interest of people that is making data dynamic. These uncertain stream data (e.g. GPS data, satellite monitoring, biometric data etc.) are the resources to many emerging applications in medical science, disaster management, national security etc. These situations increase the difficulties of extracting valuable and interesting knowledge discovery from big data. Many approaches have been developed to finding frequent patterns from uncertain data. Some have been adopted to find frequent patterns from the stream of uncertain data. Due to the uncertainty and dynamic properties of data, it becomes a great challenge to find the appropriate and efficient approach that saves resource (CPU/memory). Some approach has been developed with exact calculation and some others with the probabilistic approach. But all of them suffer from either optimization (minimum resource use) or correctness (wrong data in the result set). Moreover, most of them cannot handle the stream of data that is dynamic databases. In this thesis, we proposed an efficient, correct, optimized approach for handling uncertain data stream. We have developed a probabilistic, sliding window based approach to creating complete new \emph{US-tree} that is memory efficient and optimized. This \emph{US-tree} will keep most recent meta-information \emph{U\textsuperscript{cap}} value for further mining. A comprehensive performance analysis shows that our approach scalable, correct and faster.
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

 }

\clearpage  % Abstract ended, start a new page
%% ----------------------------------------------------------------

\setstretch{1.3}  % Reset the line-spacing to 1.3 for body text (if it has changed)

% The Acknowledgements page, for thanking everyone
\acknowledgements{
\addtocontents{toc}{\vspace{.5em}}  % Add a gap in the Contents, for aesthetics

First of all, I am thankful and expressing my gratefulness to Almighty Allah who offers me His divine blessings, patient, mental and psychical strength to complete this project work. I am deeply indebted to my project supervisor Mohammad Samiullah, Lecturer, Department of Computer Science and Engineering, University of Dhaka. His scholarly guidance, important suggestions, endless patience, constant supervision, valuable criticism, and enormous amount of work for going through my drafts and correcting them, and generating courage from the beginning to the end of the research work has made the completion of the project possible.\\\\
I would like to express my deep gratitude to Dr. Chowdhury Farhan Ahmed, Associate Professor, Department of Computer Science and Engineering, for his support and help for my work with his suggestions and time. The discussions with him on various topics related my works have helped me to enrich my knowledge and conception regarding this work.\\\\
Last but not the least; I am highly grateful to my parents, my wife, sisters, family members and friends for their support and constant encouragement, which have always been a source of great inspiration for me.
}
\clearpage  % End of the Acknowledgements
%% ----------------------------------------------------------------

\pagestyle{fancy}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back


%% ----------------------------------------------------------------
\lhead{\emph{Contents}}  % Set the left side page header to "Contents"
\tableofcontents  % Write out the Table of Contents

%% ----------------------------------------------------------------
\lhead{\emph{List of Figures}}  % Set the left side page header to "List if Figures"
\listoffigures  % Write out the List of Figures

%% ----------------------------------------------------------------
\lhead{\emph{List of Tables}}  % Set the left side page header to "List of Tables"
\listoftables  % Write out the List of Tables

%% ----------------------------------------------------------------
\addtotoc{List of Algorithms}
\lhead{List of Algorithms}  % Set the left side page header to "List of Algorithms"
\listofalgorithms
%% ----------------------------------------------------------------
\setstretch{1.5}  % Set the line spacing to 1.5, this makes the following tables easier to read
\clearpage  % Start a new page
%\lhead{\emph{Abbreviations}}  % Set the left side page header to "Abbreviations"
%\listofsymbols{ll}  % Include a list of Abbreviations (a table of two columns)
%{
% \textbf{Acronym} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or \\
%\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere \\

%\textbf{} & \textbf{} \textbf{} \textbf{} \\
%}

%% ----------------------------------------------------------------
\clearpage  % Start a new page


\setstretch{1.5}  % Return the line spacing back to 1.3

\pagestyle{empty}  % Page style needs to be empty for this page
%\dedicatory{For/Dedicated to/To my\ldots}

\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics


%% ----------------------------------------------------------------
\mainmatter   % Begin normal, numeric (1,2,3...) page numbering
\pagestyle{fancy}  % Return the page headers back to the "fancy" style

% Include the chapters of the thesis, as separate files
% Just uncomment the lines as you write the chapters

\input{./Chapters/introduction} % Introduction
%%
\input{./Chapters/litereature_study} % Previous Work
%%%
\input{./Chapters/our_proposed_approach} % Proposed Approach
%%%
\input{./Chapters/result} % Performance Evaluation
%%%
\input{./Chapters/conclusion} % Conclusion



\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics
\backmatter

%% ----------------------------------------------------------------
\label{Bibliography}
\lhead{\emph{Bibliography}}  % Change the left side page header to "Bibliography"
%\bibliographystyle{unsrtnat}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\bibliographystyle{plain}
%\bibliography{mybib}
\bibliography{Bibliography}   % The references (bibliography) information are stored in the file named "Bibliography.bib"

\clearpage
~\cite{uh_mining}
~\cite{puf_growth}
~\cite{cuf_growth}
~\cite{ufp_growth}
~\cite{uf_growth}
~\cite{u_priori}
~\cite{const_01}
~\cite{apriori}
~\cite{fp_growth}
~\cite{ass_01}
~\cite{gsp}
~\cite{prefix_span}
~\cite{ds_tree}
~\cite{rps_tree}
~\cite{hup_mining}
~\cite{g_span}
~\cite{close_1}
~\cite{closet}
~\cite{closet_plus}
~\cite{tpf}
~\cite{close_2}
~\cite{charm}
~\cite{ass_02}
~\cite{ass_03}
~\cite{ass_04}
~\cite{ass_05}
~\cite{ass_06}
~\cite{ass_07}
~\cite{sqn_02}
~\cite{sqn_02}
~\cite{sqn_02}
~\cite{suf_growth}
~\cite{stream_01}
~\cite{stream_02}
~\cite{stream_03}
~\cite{stream_05}
~\cite{uncertain_01}
~\cite{uncertain_02}
~\cite{uncertain_03}
~\cite{uncertain_04}
~\cite{uncertain_05}
~\cite{uncertain_06}
~\cite{facebook}
~\cite{twitter}
\end{document}  % The End
%% ----------------------------------------------------------------